An Hypernetwork Approach to Accurately Measure Technological Innovation \bigskip\\ \textit{Methods and Results}

### 2016-02-08 Docs/WorkingPapers/methods.tex
Organisation::timeLog_tableur

More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents. Classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes. The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$. This sorting allows to compute overlaps and differences between classes in linear time by a direct comparison. To compute higher order overlaps, we have an exponential complexity in the overlap order $o$ (in $O(K^o)$) but order three appears experimentally to have cardinals smaller enough for a reasonable one-to-one technological distance computation. A class partition strategy allows to know any distance : if $o (\mathcal{C}_i,\mathcal{C}_j)$ is first order overlap between classes $i$ and $j$ and $o_2 (\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$ second order overlap (i.e. $o(\mathcal{C}_k,o(\mathcal{C}_i,\mathcal{C}_j))$, then for any class $i$,
\begin{itemize}
\item between any $p\in \mathcal{C}_i \\ \cup_{k}{o(i,k)}$, proximity is necessarily 1 (one class in common for one-class patents)
\item for any $j \neq i$
\end{itemize}

@@

Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words. Let $K_w$ the maximal number of relevant keywords per patent. If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus. More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
\]

Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$. We write $X_k = \{x_1^{(k)},\ldots ,x_{N_k}^{(k)}\}$. Exact probability distributions within sets are determined directly in $O(\sum_{k=1}^{K}{N_k})$.

>>>>

More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents. Classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes. The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$. This sorting allows to compute overlaps and differences between classes in linear time by a direct comparison. To compute higher order overlaps, we have an exponential complexity in the overlap order $o$ (in $O(K^o)$) but order three appears experimentally to have cardinals smaller enough for a reasonable one-to-one technological distance computation. A class partition strategy allows to know any distance : if $o (\mathcal{C}_i,\mathcal{C}_j)$ is first order overlap between classes $i$ and $j$ and $o_2 (\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$ second order overlap (i.e. $o(\mathcal{C}_k,o(\mathcal{C}_i,\mathcal{C}_j))$, then for any class $i$,
\begin{itemize}
\item between any $p\in \mathcal{C}_i - \cup_{k}{o(\mathcal{C}_i,\mathcal{C}_k)}$, proximity is necessarily 1 (one class in common for one-class patents)
\item for any $j \neq i$, let $\mathcal{S}_{i,j} = o(\mathcal{C}_i,\mathcal{C}_j) - \cup_{k\neq i,j} o(\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$. Then distance within $\mathcal{S}_{i,j}$ and with non-overlapping part of the classes is straightforward computed as constant among patents
\item Remaining patents within second order overlap are few enough for a reasonable computation of their respective distances.
\end{itemize}

\paragraph{Inter-class network}

The definition of a time-dependent relation between classes as size of overlap normalized by classes sizes, by $w_{i\rightarrow j} = \frac{\left| o(\mathcal{C}_i,\mathcal{C}_j) \right|}{\left| \mathcal{C}_i\right|}$, similar to the technological distance between patents with the distinction that it is here not symmetric and captures the part of class $i$ in interaction with class $j$, allows to build an inter-class network. The evolution of network structure over time may contain useful information and reinforce e.g. a typology of classes that one can obtain by classifying temporal class trajectories.

@@

Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words. Let $K_w$ the maximal number of relevant keywords per patent. If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $k\cdot N$ keywords on the whole corpus (and take a fixed value $k=4)$, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of cooccurrences of the stem, compared to an uniform distribution within the whole corpus. More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
\]

One issue arising when working with large corpuses is the square complexity for determining cooccurrences, that can be simplified at best to the sum of squared sizes of pre-relevant keywords for each patent.

%Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$. We write $X_k = \{x_1^{(k)},\ldots ,x_{N_k}^{(k)}\}$. Exact probability distributions within sets are determined directly in $O(\sum_{k=1}^{K}{N_k})$.
